\documentclass[10pt,a4paper,ragged2e,withhyper]{imports/altacv}

\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

\usepackage{paracol}

\iftutex
  % If using xelatex or lualatex:
  \setmainfont{Lato}
\else
  % If using pdflatex:
  \usepackage[default]{lato}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
% \colorlet{name}{black}
% \colorlet{tagline}{PastelRed}
\colorlet{heading}{VividPurple}
\colorlet{headingrule}{VividPurple}
% \colorlet{subheading}{PastelRed}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change some fonts, if necessary
% \renewcommand{\namefont}{\Huge\rmfamily\bfseries}
% \renewcommand{\personalinfofont}{\footnotesize}
% \renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
% \renewcommand{\cvsubsectionfont}{\large\bfseries}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\cvItemMarker}{{\small\textbullet}}
\renewcommand{\cvRatingMarker}{\faCircle}
% ...and the markers for the date/location for \cvevent
% \renewcommand{\cvDateMarker}{\faCalendar*[regular]}
% \renewcommand{\cvLocationMarker}{\faMapMarker*}


\input{imports/pubs-num.tex}


\addbibresource{imports/sample.bib}

\begin{document}

\name{Atharva Khaire}
\tagline{}

\personalinfo{
  \email{test@gmail.com}
  \phone{1234567890}
  \mailaddress{abc}
  \linkedin{google.com}
  \github{github.com}
  \printinfo{\faLanguage}{English, Hindi}
}

\makecvheader

\columnratio{0.6}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}

\cvsection{Professional Summary}

\begin{itemize}
\item Proficient in leveraging AWS cloud services to design and implement scalable data solutions, enhancing operational efficiency and reducing costs.
\item Skilled in developing and deploying applications using Langchain and Langgraph, driving innovation in data processing and analysis.
\end{itemize}

\cvsection{Experience}

\cvevent{AI Data Engineer}{Oro AI}{2025-01-06 -- 2025-01-10}{Remote}
\begin{itemize}
\item Developed and implemented robust data pipelines using Airflow to automate workflows, ensuring timely and accurate data processing across various platforms.
Leveraged AWS services to design and deploy scalable cloud-based solutions, optimizing resource utilization and enhancing system performance.
\end{itemize}

\divider

\medskip

\cvsection{Education}

\cvevent{MS in ADA}{BU}{2025-01-06 -- 2025-01-10}{}

\divider


%% Switch to the right column. This will now automatically move to the second
%% page if the content is too long.
\switchcolumn

\cvsection{Certifications}

\cvevent{abc}{xyz}{2025-01-08}{}

\divider


\cvsection{Skills}

\cvtag{AWS}
\cvtag{Langchain}
\cvtag{Airflow}
\cvtag{Python}
\cvtag{MongoDB}
\cvtag{SQL}
\cvtag{Pinecone}

\medskip

\cvsection{Achievements}

\begin{itemize}
\item Achieved a specialization in Advanced Data Analytics (ADA), demonstrating a strong foundation in data-driven decision-making and analytical skills essential for a career in data science.
\item Completed coursework in Python programming, equipping with the ability to develop robust data analysis tools and automate processes, aligning with industry standards.
\item Gained proficiency in AWS, enhancing cloud computing skills necessary for deploying scalable data solutions and managing large datasets effectively.
\item Studied PySpark, enabling the ability to handle big data processing and analytics, which is crucial for roles focused on data engineering and analysis.
\item Explored Langchain, fostering skills in building applications that utilize language models, preparing for innovative roles in AI and machine learning.
\item Consistently maintained a high academic performance, reflecting dedication and a strong work ethic, which are vital for success in fast-paced professional environments.
\end{itemize}

\medskip

\end{paracol}
\end{document}
